Case study validations of automatic bullet matching

### 2018-11-20 index.Rmd
reorder

The cross-correlation (CC) function between two signatures $S_1(x)$ and $S_2(x)$ is defined as \[CC(S_1, S_2, z) = \text{cor}\left(S_1(x), S_2(x + z)\right)\] where \hh{$x$ and $x+z$ are integer values appropriately defined within the domains of $S_1$ and $S_2$ and  $z$ is the lag between the two sequences. The lag $z$ used to achieve maximum $CC$ is used to determine the best alignment; the maximal value of $CC$ is  used to assess the match strength between the two sequences.} When signatures contain missing values, pairwise complete observations are used to calculate the cross-correlation.

@@

<!-- \hh{XXX define signatures mathematically here - as random spatial process; extracted from crosscut by removing big structure first and then applying (cross-validated, \citet{aoas}) 'roughness' filter. 'roughness' defined by NIST paper. } -->

@@

One of the measures firearms examiners use to describe the strength of a match quantitatively is the number of consecutive matching striae (CMS) as defined by \citet{biasotti}.
If there are at least 6 consecutive matching striae, the bullets are considered to be a good match \citep{biasotti_firearms_1997,nichols_scientific_2006}. 
CMS in this setting are counted as the number of consecutive peaks in signatures of two lands that match, in part because it is difficult to visually assess valleys except as relative to peaks. 
Note that because signatures are moved into phase based on the maximum cross-correlation rather than matching striation marks, it is possible for two lands to have a consecutive matching striae of 0. CMS are generally considered to be a very conservative criteria, in that bullets fired through the same barrel may not have a high number of consecutively matching striae; in this sense, CMS may be more likely to produce an inconclusive result.
<!--\hh{XXX for CMS we need to define peaks, and matching peaks, and for that we need to define the additional filter/smooth.}\svp{XXX Can't we just refer to the aoas paper? It seems to be defined in there relatively well.}-->
\svp{XXX Feels like we need to mention something about ccf here just because these are the 3 main features we're using to evaluate the algorithm...?}

@@

### Land-to-Land Comparisons

@@

\svp{XXX This is a bit of an incomplete thought. I think I know where you were going, but can you expand on it a bit so that I'm not putting words in your mouth? XXX}
\citet{Morrison:2018km}  stress the need to additionally include the typicality of a signature.

>>>>

The cross-correlation (CC) function between two signatures $S_1(x)$ and $S_2(x)$ is defined as \[CC(S_1, S_2, z) = \text{cor}\left(S_1(x), S_2(x + z)\right)\] where \hh{$x$ and $x+z$ are integer values appropriately defined within the domains of $S_1$ and $S_2$ and  $z$ is the lag between the two sequences. When signatures contain missing values, pairwise complete observations are used to calculate the cross-correlation. The lag $z$ used to achieve maximum $CC$ is used to determine the best alignment.}

@@

@@

One of the measures firearms examiners use to describe the strength of a match quantitatively is the number of consecutive matching striae (CMS) as defined by \citet{biasotti}. \svp{In order to evaluate CMS, we must first identify peaks and valleys in each of the signatures, then determine whether these peaks and valleys overlap sufficiently. Features which firearms examiners assess visually depend on the identification of these extrema; numerical features such as cross-correlation can be computed from the aligned signatures alone. }

If there are at least 6 consecutive matching striae, the bullets are considered to be a good match \citep{biasotti_firearms_1997,nichols_scientific_2006}. 
CMS in this setting are counted as the number of consecutive peaks in signatures of two lands that match, in part because it is difficult to visually assess valleys except as relative to peaks. 
Note that because signatures are moved into phase based on the maximum cross-correlation rather than matching striation marks, it is possible for two lands to have a consecutive matching striae of 0. CMS are generally considered to be a very conservative criteria, in that bullets fired through the same barrel may not have a high number of consecutively matching striae; in this sense, CMS may be more likely to produce an inconclusive result.
<!--\hh{XXX for CMS we need to define peaks, and matching peaks, and for that we need to define the additional filter/smooth.}\svp{XXX Can't we just refer to the aoas paper? It seems to be defined in there relatively well.}-->
\svp{XXX Feels like we need to mention something about ccf here just because these are the 3 main features we're using to evaluate the algorithm...?}

; the maximal value of $CC$ is  used to assess the match strength between the two sequences

@@

### Bullet Structure

@@
